%basic cover letter template
\documentclass{letter}
%\usepackage{amssymb,amsmath}
\usepackage{graphicx}

\oddsidemargin=.2in
\evensidemargin=.2in
\textwidth=5.9in
\topmargin=-.3in
\textheight=9in
\signature{Dhruv Mohindru}
\address{\bf Dhruv Mohindru \\ \bf dmohindru@gmail.com \\  \bf 0411910745 \\ \bf Westmead, NSW}

\longindentation=0pt

\begin{document}
%%%% Modify Company to be addressed
\begin{letter}{\bf Revolution IT\\Level 1, St Andrews House,\\Sydney NSW\\Australia}
%%%%

%%%% Add name of Hiring Manager
\opening{Dear Hiring Manager,\\}
%%%%

%%%% Modify Job title or description here
RE: Software Engineer
%%%%

%%%% Point three - Modify this paragraph according to job tile/description

I am writing to apply for the position of Software Engineer, which was advertised on JobActive.
%%%%%% Point three ends here

%%%% Point four why you should be selected for this role

About myself, being an out-of-box thinker, creative and passionate about technology helps me come up with very innovative solutions. A keen learner of new technologies and always looking for challenges to apply newly acquired skills.
%%%%

I have enclosed my resume to support my application. It is evident that I would bring skills and experience to position, including\\
%%%% Point five high l1ight relevant part of resume
\begin{itemize}
\item Translating requirements into a technical design.
\item Developing front-end and back-end of an application.
\item Develop Rest API for inter-departmental data access.
\item Designing database (SQL and NoSQL) to support business processes.
\item Integrating backend systems with frontend systems.
\item Containerizing final product.
\end{itemize}
%%%%

%%%% Point six - Match your skills directly to the job you're applying for.
I believe my skills are perfectly tailored for this job, as I have good experience in understanding business processes and converting requirements into technical design, and developing business process workflow applications.
%I believe my skills are perfectly tailored for this job, as I have good experience in building decoupled system and exposing their data and functionality through API.
%%%%

%%%% Point seven - Show that you have researched the company and are passionate about what they do.
%I really liked Livn's API Direct and API Wholesales products which I feel is a perfect way of integrating with external systems and generate revenue stream. This is a kind of work I had always loved to do and would be happy to assist Livn. 
%%%%


%%%% Point eight - Call to action
I would value the opportunity to talk about this role and how can I bring value to your organization.   
Thank you for considering my application. I look forward to hear from you.
%%%%




\closing{Sincerely,
} 

\end{letter}
\end{document}

